\documentclass [11pt,a4paper]{moderncv}
\usepackage{multicol}
\usepackage[scale=0.75]{geometry}

\moderncvtheme[blue]{classic}
% colors include blue, orange, green, red, purple, grey, and black
% styles casual, classic, oldstyle, banking

%\nopagenumbers{} %used to remove line numbers

%----------------------------------------
% Personal Data
%----------------------------------------

\firstname{Ian}
\lastname{Westrope}
\title{Software Engineer}
%\address{1529 Basin St SW}{} home address
%\address{514 S Polk St}{Apt 5}{Moscow, ID 83843}
\mobile{+1~(509)~398~6256}
\email{ian.westrope@gmail.com}
%\homepage{www.github.com}
\social[github]{westrope}


%----------------------------------------
% Content
%----------------------------------------

\begin{document}
\makecvtitle

\section{Education}
% BA
\cventry{2010--2015}{Bachelor of Science in Computer
  Science}{University of Idaho}{Moscow, ID}{\textit{GPA:
    3.14}}{Relevant Coursework:\vspace{-5mm}\begin{multicols}{2}
  \begin{itemize}
  \item Compiler Design
  \item Data Structures
  \item Programming Languages
  \item Technical Writing
  \item Analysis of Algorithms
  \item Object Oriented Design
  \item Operating Systems
  \item Computer Graphics
  \item System Software
  \item Software Engineering
  \item Database Systems
  \item Theory of Computation
  \item Evolutionary Computation
  \item Video Games and Evolution
%  \item Engineering Physics
  \item Probability and Statistics
  \item Linear Algebra
  \item Differential Equations
  \item Calculus
  \item Discrete Math
  \item Computer Organization and Architecture
%  \item Senior Design Project    
\end{itemize}
\end{multicols}}% arguments 3 to 6 can be left empty


% AA
\cventry{2008--2010}{Associates in Arts and Science}{Big Bend Community
  College}{Moses Lake, WA}{\textit{GPA: 3.70}}{Completed degree concurrently
  with High School Diploma}
% arguments 3 to 6 can be left empty
% Relevant Coursework

\section{Experience}

\cventry{2015--Present}{Unicon Research Assistant}{Dr. Clinton
  Jeffery}{Moscow, ID}{}{
  \begin{itemize}
  \item Remodeled garbage collection to be concurrent.
  \item Edited existing technical reports.
  \item Prepared code to be merged into master branch.
  \end{itemize}}
%possibly make this description into bullet points

\cventry{Summer 2014--2015}{Student Athlete Tutor}{University of
  Idaho}{Moscow, ID}{}{Tutored students in:
  \begin{itemize}
  \item Math
  \item Computer Science
  \item Logic
  \end{itemize}}

\cventry{Summer 2013}{Pool Manager}{SplashZone City
  Pool}{Ephrata, WA}{}{
  \begin{itemize}
  \item Managed daily pool functions, shift scheduling for 40
    employees.
  \item Trained pool staff in lifeguarding skills and safety.
  \item Reconciled money daily.
  \item Provided customer service for pool patrons.
\end{itemize}}

\cventry{Summer 2010--2012}{Lifeguard/Head Lifeguard}{SplashZone City
  Pool}{Ephrata, WA}{}{
  \begin{itemize}
  \item Responded to emergency situations.
  \item Instructed swimming lessons.
  \item Promoted to Head Lifeguard.
    \begin{itemize}
 %   \item Oversaw Pool Aids.
    \item Instructed new Lifeguards.
    \item Helped open and close pool.
    \end{itemize}
  \end{itemize}}
%research assistant

\section{Skills}
\begin{cvcolumns}
  \cvcolumn{Proficient With}{
    \begin{itemize}
    \item C
    \item C++
    \item Git and GitHub
    \item Make
    \item \LaTeX
    \item Bash
    \item Flex
    \item Bison
    \end{itemize}
  }
  \cvcolumn{Experience With}{           
    \begin{itemize}
    \item Java
    \item Processing
    \item Python
    \item Common Lisp
    \item Unicon
    \item Agile Development
    \end{itemize}
  }
  \cvcolumn{Interested In}{
    \begin{itemize}
    \item Ruby
    \item SQL
    \item Objective C
    \item JavaScript
    \end{itemize}
  }
\end{cvcolumns}
% Proficient In
% Expirience with
% Interested In

\section{Projects}

\cvitem{Unicon Development}{
  \begin{itemize}
  \item Added concurrency functionality to the Unicon optimizing compiler.
  \item Worked with a large codebase.
  \item Presented a poster and gave a technical presentation at Engineering Expo 2015.
  \end{itemize}}\vspace{-3mm}

\cvitem{Evolutionary Computation}{
  \begin{itemize}
  \item Implemented evolutionary algorithms using C++11.
  \item Utilized basic hill climbing, genetic algorithms, and genetic
    programming to solve problems including function regression,
    k--satisfiability solver, simple cipher solver.
  \item Optimized using bit manipulation.
\end{itemize}}\vspace{-3mm}

\cvitem{EvolveTD}{
  \begin{itemize}
  \item Collaborated between computer scientists and biologists to
    create a tower defense game with realistic evolution of the
    attacking creatures.
  \item Developed a scent communication between the creatures.
  \item Conducted a hypothesis test and created an educational activity.
\end{itemize}}\vspace{-3mm}

\cvitem{Swords and Sorcery}{
  \begin{itemize}
  \item Created a computerized version of Swords and Sorcery.
  \item Collaborated with 17 people using agile development methods.
  \item Developed recursive algorithm to show users how far they could
    move over varying terrain types.
  \item Created class diagrams and use cases.
  \item Wrote technical documentation.
\end{itemize}}\vspace{-3mm}

\cvitem{120++ Compiler}{
  \begin{itemize}
  \item Created a compiler for a subset of C++ called 120++.
  \item Used C, flex, and bison.
  \item Performed lexical, syntax, and semantic analysis.
\end{itemize}}\vspace{-3mm}

% Uniconc poster and presentation
% Paper with Dr. J
% EvoComp
% 404
% Software Engineering

%\section{Experience}
%research assistant 
%tutor
%Pool managar


\section{Involvement}
\cvlistitem{Volunteered for Saturday of Service at a children's carnival.}
\cvlistitem{Volunteered to convert the Kibbie Dome from football to basketball.}
\cvlistitem{Volunteered to set up for Finals Fest concert.}
\cvlistitem{Member of University Climbing Team.}
%climbing club
%volunteer work with club
%saturday of service





\end{document}


